---
title: "MSDB Stereology analysis"
author: "Iris Oren & Anne-Laure Hemonnot"
date: "09 August 2017"
output: html_document
---

The summary sheet of .xslx output files from steroinvestigator are saved as .csv.

All.csv files from all animals are stored in the /Data subdirectory from the project folder

Genotypes decoding spreadsheet with variables:  |ID|Genotype| saved in /Data/Genotypes/GenotypeDat.csv (filename can be changed in Initialisation_Chunk, but the csv file should not be stored in the main Data directory)

User specifies User line - Region mapping in Initialisation_Chunk. More userlines can be added

```{r Initialisation_Chunk, echo=FALSE}
#Script to import data and analyse the output of stereoinvestigator in R
#NOTE: Before this is run for the first time, need to run "install.packages("stringr")
#Iris Oren: 100816

source("./R/ImportFromStereoInvestigator.R")
source("./R/GetID.R")
library(stringr)

#User to specify userlines and corresponding regions
UserLines <- data.frame(
  Region= c("User Line 1", "User Line 2"), 
  RegionVar=c("MS", "DB"))

#Specify name of data directory
DataDir <- "Data"
#Specify Genotypes filename
GenotypeFilename <-"./Data/Genotypes/GenotypeDat.csv"
#Specify saving directory
OutputDir <- "./Output/"
```

Import the data and add variables for genotype and regions  in ImportAndPrepare_Chunk and 
```{r ImportAndPrepare_Chunk, echo=FALSE}
#Import all .csv datafiles in the working directory
DataAll <- ImportFromStereoInvestigator(DataDir)
#Add a variable for ID based on Filename in the format "[A-Z0-9]". This gives an error which can be ignored
DataAll$ID <- GetID(DataAll$DataFile)
#Add regions to the data frame
DataAll <- merge(x=DataAll, y=UserLines, by="Region", all.x = TRUE)
#############
#Add genotype information
# Merge by animal ID: http://stackoverflow.com/questions/1299871/how-to-join-merge-data-frames-inner-outer-left-right
# GenotypeDat.csv should be saved in Data/Genotypes/GenotypeDat.csv
#File structure: |ID|Genotype|
#UNCOMMENT THE LINES BELOW WHEN WE HAVE THE GENOTYPE INFO
GenotypeDat <- read.table(GenotypeFilename, sep=",", header=TRUE)
### Change the number of digit for sample ID ### 
# Define the column to modify
# Define the number of digit with "%numberd"
# Select the concerned column with filename[, col] function
GenotypeDat$ID <- sprintf("%02d", GenotypeDat[, 1])
DataAll <- merge(x=DataAll, y=GenotypeDat, by="ID", all.x=TRUE)
#####################
```



Save the full dataframe
```{r SaveDataFrame_Chunk, echo=FALSE}
dir.create(OutputDir, showWarnings = FALSE)
FullFileName <- paste(OutputDir, "DataAll", sep="")
write.csv2(DataAll, file=FullFileName)
```

This is a Brain Slice showing (i) the staining and (ii) how we determined the junction between MS and DB

```{r BrainSectionStaining_Chunk, echo=FALSE}
#Uncomment the next line if you need this package 
install.packages("png", repos='http://cran.us.r-project.org')
library(png)
img = readPNG("Brain_Example.png")
grid::grid.raster(img)
```



We visualize the useful data table 

```{r Data_Chunk, echo=FALSE}
data.frame(DataAll$EstPopUserDefThickness, DataAll$Genotype, DataAll$RegionVar)
```


Now we analyse the data, we want to know if there is a significant variation between AD treated and WT treated mice. 

```{r GraphsMaking1_Chunk, echo=FALSE}
##### Graph of estimated population in function of genotype ######
# Uncomment first and last lines to save the image as a .png 
#png(file="EstimatedPopulation_Genotype_Graph.png",width=450,height=350)
  plot(DataAll$Genotype, 
       DataAll$EstPopUserDefThickness, 
       main="Correlation between genotype \n and estimated population", 
       col.main="black", 
       ylab="Estimated Population")
#dev.off()
```



```{r GraphsMaking2_Chunk, echo=FALSE}
# Graph of ChAT estimated population in function of genotype and seperated depending on region
# Uncomment line png to save the graph as a .png 
#png(file="Population_inFunctionOf_Genotype_RegionVar.png", width=450, height=400)
par(mar=c(9,6,4,2))
# I increase the bottom margin to visualise the full xlable
boxplot(DataAll$EstPopUserDefThickness~DataAll$RegionVar*DataAll$Genotype,
        data=DataAll, 
        notch=FALSE,
        las=2,
        col=(c("white","light grey")),
        main="CHAT Estimated population \n depending on genotypes and region",
        xlab="", 
        ylab="Estimated population")
#dev.off()
```

This representation shows :

Mean in bold, 

Standard deviation for error bars. 

```{r GraphsMaking3_Chunk, echo=FALSE}
#Graph of ChAT estimated population in function of genotype and seperated depending on region
#Uncomment lines to save the graph in .png 
Region <- DataAll$RegionVar
#png(file="Title.png",width=450,height=350)
interaction.plot(DataAll$Genotype, Region, DataAll$EstPopUserDefThickness, 
    main="Region dependant population variation \n in fonction of genotype",
    xlab = "", 
    ylab = "Estimated population")
#dev.off()
```

This representation shows that there is a more numerous ChAT interneurons population in the DB than the MS in WT mice whereas for treated mice (AD and WT) they seem to have a reduced DB population and increased MS population. 

However there is an aberrant data on line 17 for an WT-MS value, I exclude it to visualize new graphs 

```{r GraphsMaking4_Chunk, echo=FALSE}
# Graph of ChAT estimated population in function of genotype and seperated depending on region
# Uncomment line png to save the graph as a .png 
#png(file="Population_inFunctionOf_Genotype_RegionVar.png", width=450, height=400)
DataAll2 <- DataAll[-17,]
# I exclude the aberrant value 
par(mar=c(9,6,4,2))
# I increase the bottom margin to visualise the full xlablel
boxplot(DataAll2$EstPopUserDefThickness~DataAll2$RegionVar*DataAll2$Genotype,
        data=DataAll2, 
        notch=FALSE,
        las=2,
        col=(c("white","light grey")),
        main="CHAT Estimated population \n depending on genotypes and region",
        xlab="", 
        ylab="Estimated population")
#dev.off()
```


```{r GraphsMaking5_Chunk, echo=FALSE}
#Graph of ChAT estimated population in function of genotype and seperated depending on region
#Uncomment lines to save the graph in .png 
Region <- DataAll2$RegionVar
#png(file="Title.png",width=450,height=350)
interaction.plot(DataAll2$Genotype, Region, DataAll2$EstPopUserDefThickness, 
    main="Region dependant population variation \n in fonction of genotype",
    xlab = "", 
    ylab = "Estimated population")
#dev.off()
```


In conclusions: 

CHAT + neuron total number is similar between the three groups if we look at graph#1 

CHAT + neuron number varies depending on the region in WT sections with a higher number un DB vs MS 

This regionalisation looks reduced by Donepezil but is not significant (I haven't done any statistics on it but by seeing the error bars I am quite sure it will not be different)





```{r Knitting_Chunk, echo=FALSE}
## For knitting I needed an older version of R so I changed it 
#packageurl <- "http://cran.r-project.org/src/contrib/Archive/knitr/knitr_1.12.tar.gz"
#install.packages(packageurl, repos=NULL, type="source")
```
