---
title: "MSDB Stereology analysis"
author: "Iris Oren"
date: "12 August 2016"
output: html_document
---

The summary sheet of .xslx output files from steroinvestigator are saved as .csv.

All.csv files from all animals are stored in the /Data subdirectory from the project folder

Genotypes decoding spreadsheet with variables:  |ID|Genotype| saved in /Data/Genotypes/GenotypeDat.csv (filename can be changed in Initialisation_Chunk, but the csv file should not be stored in the main Data directory)

User specifies User line - Region mapping in Initialisation_Chunk. More userlines can be added

```{r Initialisation_Chunk, echo=FALSE}
#Script to import data and analyse the output of stereoinvestigator in R
#NOTE: Before this is run for the first time, need to run "install.packages("stringr")
#Iris Oren: 100816

source("./R/ImportFromStereoInvestigator.R")
source("./R/GetID.R")
library(stringr)

#User to specify userlines and corresponding regions
UserLines <- data.frame(
  Region= c("User Line 1", "User Line 2"), 
  RegionVar=c("MS", "DB"))

#Specify name of data directory
DataDir <- "Data"
#Specify Genotypes filename
GenotypeFilename <-"./Data/Genotypes/GenotypeDat.csv"
#Specify saving directory
OutputDir <- "./Output/"
```

Import the data and add variables for genotype and regions  in ImportAndPrepare_Chunk and 
```{r ImportAndPrepare_Chunk, echo=FALSE}
#Import all .csv datafiles in the working directory
DataAll <- ImportFromStereoInvestigator(DataDir)
#Add a variable for ID based on Filename in the format "[A-Z0-9]". This gives an error which can be ignored
DataAll$ID <- GetID(DataAll$DataFile)
#Add regions to the data frame
DataAll <- merge(x=DataAll, y=UserLines, by="Region", all.x = TRUE)
#############
#Add genotype information
# Merge by animal ID: http://stackoverflow.com/questions/1299871/how-to-join-merge-data-frames-inner-outer-left-right
# GenotypeDat.csv should be saved in Data/Genotypes/GenotypeDat.csv
#File structure: |ID|Genotype|
#UNCOMMENT THE LINES BELOW WHEN WE HAVE THE GENOTYPE INFO
GenotypeDat <- read.table(GenotypeFilename, sep=",", header=TRUE)
### Change the number of digit for sample ID ### 
# Define the column to modify
# Define the number of digit with "%numberd"
# Select the concerned column with filename[, col] function
GenotypeDat$ID <- sprintf("%02d", GenotypeDat[, 1])
DataAll <- merge(x=DataAll, y=GenotypeDat, by="ID", all.x=TRUE)
#####################
```



Save the full dataframe
```{r SaveDataFrame_Chunk, echo=FALSE}
dir.create(OutputDir, showWarnings = FALSE)
FullFileName <- paste(OutputDir, "DataAll", sep="")
write.csv2(DataAll, file=FullFileName)
```

Now we analyse the data, we want to know if there is a significant variation between AD treated and WT treated mice. 

```{r GraphsMaking_Chunk, echo=FALSE}
# Histogram of ChAT estimated population in function of genotype and seperated depending on region
# Uncomment line ggsave to save the graph as a .png 
# Uncomment next line if needed 
#install.packages("ggplot2")
library(ggplot2)
BrainRegion <- DataAll$RegionVar
plot_data <- ggplot(DataAll, 
       aes(x=DataAll$Genotype, y=DataAll$EstPopUserDefThickness, fill=BrainRegion)) + geom_bar(aes(y=DataAll$EstPopUserDefThickness), 
       stat="identity", position="dodge")
plot_data+labs(title="ChAT Positive Interneurons ", x="", y = "Estimated Population")+
  theme_classic() +
  scale_fill_manual(values=c('#AFB5B4','#59D9C8'))
#ggsave(plot=plot_data, file="ADD_NAME.png")

#Graph of ChAT estimated population in function of genotype and seperated depending on region
#Uncomment lines to save the graph in .png 
Region <- DataAll$RegionVar
#png(file="Title.png",width=450,height=350)
interaction.plot(DataAll$Genotype, Region, DataAll$EstPopUserDefThickness, 
    main="Region dependant population variation \n in fonction of genotype",
    xlab = "", 
    ylab = "Estimated population")
#dev.off()
```

The last representation shows that there is a more numerous ChAT interneurons population in the DB than the MS in WT mice whereas for treated mice (AD and WT) they seem to have a reduced DB population and increased MS population.  


